Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
copyedit FeatureUnion description
Select only 10 features, which is more likely to actually work
when PCA and KernelPCA get to determine their numbers of components
automatically.

A \texttt{FeatureUnion} object is a transformer combining multiple transformers
into a single one that joins their outputs. From an API point of view, a
\texttt{FeatureUnion} takes as input a list of transformers. Calling
\texttt{fit} on the union is the same as calling \texttt{fit} independently on
each of the transformers. For transforming data, the base transformers are
applied in parallel and their outputs are concatenated end-to-end into a larger
output.

As an example, the following snippet illustrates how to create a complex worflow
computing both linear PCA and kernel PCA components on \texttt{X\_train}
(through a \texttt{FeatureUnion}),
selecting the 100 best of those features according to an ANOVA test
and then feeding them to an $\ell_2$-regularized logistic regression model:
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA
from sklearn.feature_selection import SelectKBest
from sklearn.linear_model import LogisticRegression

@@

Pipeline([("feat_union", fu),
          ("feat_sel", SelectKBest(k=100)),
          ("log_reg", LogisticRegression(penalty="l2"))
]).fit(X_train, y_train).predict(X_test)
\end{pythoncode}

As the above example shows, \texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex and nested workflows.

>>>>

A \texttt{FeatureUnion} object is a transformer combining multiple transformers
into a single one that concatenates their outputs,
in the sense that a union of transformers that map inputs having $d$ features
to $d'$ and $d''$ features, respectively,
is a transformer that maps its $d$ input features to $d' + d''$ features
by calling its underlying transformers in parallel.
From an API point of view, a
\texttt{FeatureUnion} takes as input a list of transformers. Calling
\texttt{fit} on the union is the same as calling \texttt{fit} independently on
each of the transformers.

As an example, the following snippet illustrates how to create a complex worflow
computing both linear PCA and kernel PCA components on \texttt{X\_train}
(through a \texttt{FeatureUnion}),
selecting the 10 best of those features according to an ANOVA test
and then feeding them to an $\ell_2$-regularized logistic regression model:
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA
from sklearn.feature_selection import SelectKBest
from sklearn.linear_model import LogisticRegression

@@

Pipeline([("feat_union", fu),
          ("feat_sel", SelectKBest(k=10)),
          ("log_reg", LogisticRegression(penalty="l2"))
]).fit(X_train, y_train).predict(X_test)
\end{pythoncode}
As the above example shows, \texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex and nested workflows.
